---
title: "Car presentation"
author: "Kipchumba Brian"
date: "3/23/2021"
output: ioslides_presentation
---


## My Reproducible Pitch

### See the Regression Models Course Project  

- mygithubub: *https://github.com/Briannobert/shiny_projesct*
- Using this Mtcars dataset i created a Shiny application and deployed it to my R server .I had to register first
- I credit my summary to 
```{r}
?mtcars
```


---

## mtcars Dataset

### Motor Trend Car Road Test

-The data was extracted from the 1974 Motor Trend US magazine, and comprises fuel consumption and 10 aspects of automobile design and performance for 32 automobiles (1973-74 models).
### Source

```{r}
library(datasets)
head(mtcars, 5)
```
---

##Note

-Henderson and Velleman (1981) comment in a footnote to Table 1: ‘Hocking [original transcriber]'s noncrucial coding of the Mazda's rotary engine as a straight six-cylinder engine and the Porsche's flat engine as a V engine, as well as the inclusion of the diesel Mercedes 240D, have been retained to enable direct comparisons to be made with previous analyses.’

## Mtcars Dataset - Format

**A data frame with 32 observations on 11 variables.**

| Index | Field | Detail |
------- | ----- | ------ |
| [, 1] | mpg | Miles/(US) gallon |
| [, 2]  | cyl | Number of cylinders |
| [, 3]	| disp | Displacement (cu.in.) |
| [, 4]	| hp | Gross horsepower |
| [, 5]	| drat | Rear axle ratio |
| [, 6]	| wt | Weight (lb/1000) |
| [, 7]	| qsec | 1/4 mile time |
| [, 8]	| vs | V/S |
| [, 9]	| am | Transmission (0 = automatic, 1 = manual) |
| [,10]	| gear | Number of forward gears |
| [,11]	| carb | Number of carburetors |

---

## Main Analysis  Code

```{r
  FTP <- reactive({
    paste("mpg ~", "as.integer(", input$variable, ")")  })
  
  fit <- reactive({
    lm(as.formula(FTP()), data=mpgData)  })
  ...
  output$fit <- renderPrint({
    summary(fit()) })
  
  output$mpgPlot <- renderPlot({
    with(mpgData, {
      plot(as.formula(FTP()))
      abline(default(), col=2)
    })  })
```
##source

-Henderson and Velleman (1981), Building multiple regression models interactively. Biometrics, 37, 391–411.
